\\Large The heat is on: Rising temperatures alter when, how, and where large terrestrial mammals move

### 2025-06-11 writing/appendix-b-gams.Rmd
capped max SE to 3

```{r hrsf-se, fig.cap="Estimated standard error in the relative selection strength (RSS) for forest cover (\\%), elevation (km), and distance from water (km) as a function of temperature (see Fig. 3 in the main text). The grey contours indicate the extent of each speices' observed locations."}
knitr::include_graphics('../figures/hrsf-surface-plots-se.png')
```

>>>>

```{r hrsf-se, fig.cap="Estimated standard error in the relative selection strength (RSS) for forest cover (\\%), elevation (km), and distance from water (km) as a function of temperature (see Fig. 3 in the main text). The grey contours indicate the extent of each speices' observed data. For ease of readability, the color bar values were capped to a maximum of 3 (original maximum was 7.00)."}
knitr::include_graphics('../figures/hrsf-surface-plots-se.png')
```
